### 2014-06-04 paper/paper.tex
Sanaz changes for revision 1 in

However, there are some cases where it cannot be said that $\vec x \preceq \vec y$ or $\vec y \preceq \vec x$. 
In this case, it is said that these solutions are non-dominated with respect to each other. Solutions that are not dominated can be grouped in a \textit{non-dominated set}. Given a non-dominated set $P$, it is said that $P$ is the \textit{Pareto-set} if there is no other solution in the decision space that dominates any member of $P$. The corresponding objective vectors of the members in the Pareto-set build a so called \textit{Pareto-front}. The relations between decision and objective space, dominance and the non-dominated set are depicted in Figure~\ref{fig:moop}.

@@

A popular choice for multi-objective optimization problems are evolutionary multi-objective optimization (EMO) algorithms~\cite{Coello1999, Zhou2011}. 
The goal of EMO algorithms is to find a set of optimal solutions with a good convergence to the Pareto-front as well as a good spread and diversity along the Pareto-front.
One of the most well-known algorithms in the literature is the Non-dominated Sorting Evolutionary Algorithm II (NSGA-{II})~\cite{Deb2002}, the pseudocode of which is shown in Algorithm~\ref{alg:nsga2}. As in any evolutionary algorithm, NSGA-{II} evolves a set of $N$ individuals in a population denoted as $Pop$ with the difference that they are ranked according to a dominance criterion and a crowding distance measure, which are used to maintain a good diversity of solutions. After each iteration of the algorithm, only the best $N$ individuals according to this ranking are maintained to the next generation.

@@

The three main pillars of the NSGA-2 algorithm are:
\begin{itemize}
\item Fast non-dominated sorting: The function $F = \Call{fastNonDominatedSort}{U(t)}$ performs a non-dominated sorting and ranks the individuals stored in a set $U$ into several non-dominated fronts denoted as $F_i$, where the solutions in $F_0$ are the non-dominated solutions in the entire set. $F_i$ is the set of non-dominated solutions in $R \setminus (F_0 \cup \cdots \cup F_{i-1})$. 
\item Crowding distance: The function $\Call{crowdingDistanceAssignment}{F_i}$ assigns to each one of the individuals in $F_i$ a crowding distance value, which is the distance between the individual and its neighbours. The individuals with the smallest crowding distances are selected with a lower probability than the ones with larger values.   
\item Elitism: The individuals from the first front $F_0$ are always ranked first, according to the dominance criterion and their crowding distance. This ensures that the best solutions always survive to the next generation.
\end{itemize}

@@

\begin{table}[!t]
\begin{center}
%\begin{tabular}{|>{\centering\arraybackslash}m{0.65cm}|c|c|c|c|}
\begin{tabular}{|p{0.8cm}|p{2.2cm}|m{1.13cm}|m{1.13cm}|m{1.13cm}|}
\hline
\textbf{Map}  & \textbf{$W:(w_t, w_f, w_d)$} & \textbf{Time} &  \textbf{Fuel} & \textbf{Damage} \\ 
\hline
 \multirow{3}{*}{\textbf{Map 1}} & $(0.33,0.33,0.33)$ & $1654 \pm 7$ & $131 \pm 2$& $846 \pm 13$\\
 & $(0.1,0.3,0.6)$ & $1657 \pm 8$ & $130 \pm 2$ & \bm{$773 \pm 11$}\\
 & $(0.1,0.6,0.3)$ & $1681 \pm 11$ & $131 \pm 2$ & $837 \pm 15$\\
 & $(0.6,0.1,0.3)$ & $1649 \pm 8$ & $132 \pm 2$ & $833 \pm 13$\\
\hline
 \multirow{3}{*}{\textbf{Map 2}} & $(0.33,0.33,0.33)$ & $1409 \pm 7$ & $235 \pm 4$& $364 \pm 3$\\
 & $(0.1,0.3,0.6)$ & $1402 \pm 6$ & $236 \pm 5$ & \bm{$354 \pm 2$}\\
 & $(0.1,0.6,0.3)$ & $1416 \pm 8$ & \bm{$219 \pm 4$} & $360 \pm 3$\\
 & $(0.6,0.1,0.3)$ & $1396 \pm 8$ & $245 \pm 5$ & $361 \pm 2$\\
\hline
 \multirow{3}{*}{\textbf{Map 3}} & $(0.33,0.33,0.33)$ & $1373 \pm 6$ & $221 \pm 3$& $301 \pm 7$\\
 & $(0.1,0.3,0.6)$ & $1378 \pm 5$ & $211 \pm 3$ & \bm{$268 \pm 5$}\\
 & $(0.1,0.6,0.3)$ & $1385 \pm 6$ & \bm{$203 \pm 4$} & $291 \pm 7$\\
 & $(0.6,0.1,0.3)$ & \bm{$1363 \pm 4$} & $229 \pm 4$ & $285 \pm 7$\\
\hline
 \multirow{3}{*}{\textbf{Map 4}} & $(0.33,0.33,0.33)$ & $1383 \pm 6$ & $291 \pm 5$& $565 \pm 5$\\
 & $(0.1,0.3,0.6)$ & $1385 \pm 7$ & $304 \pm 4$ & \bm{$542 \pm 4$}\\
 & $(0.1,0.6,0.3)$ & $1423 \pm 6$ & \bm{$273 \pm 4$} & $583 \pm 5$\\
 & $(0.6,0.1,0.3)$ & $1388 \pm 6$ & $309 \pm 4$ & $559 \pm 5$\\
\hline
 \multirow{3}{*}{\textbf{Map 5}} & $(0.33,0.33,0.33)$ & $1405 \pm 7$ & $467 \pm 4$& $559 \pm 4$\\
 & $(0.1,0.3,0.6)$ & $1431 \pm 9$ & $447 \pm 4$ & $541 \pm 4$\\
 & $(0.1,0.6,0.3)$ & $1467 \pm 9$ & \bm{$411 \pm 5$} & $567 \pm 5$\\
 & $(0.6,0.1,0.3)$ & $1399 \pm 9$ & $469 \pm 4$ & $547 \pm 3$\\
\hline
 \multirow{3}{*}{\textbf{Map 6}} & $(0.33,0.33,0.33)$ & $1575 \pm 7$ & $549 \pm 5$& $303 \pm 4$\\
 & $(0.1,0.3,0.6)$ & $1626 \pm 9$ & $540 \pm 6$ & $286 \pm 5$\\
 & $(0.1,0.6,0.3)$ & $1703 \pm 11$ & \bm{$499 \pm 4$} & $316 \pm 7$\\
 & $(0.6,0.1,0.3)$ & $1571 \pm 7$ & $559 \pm 5$ & $294 \pm 4$\\
\hline
 \multirow{3}{*}{\textbf{Map 7}} & $(0.33,0.33,0.33)$ & $1434 \pm 5$ & $599 \pm 6$& $284 \pm 6$\\
 & $(0.1,0.3,0.6)$ & $1475 \pm 10$ & $602 \pm 5$ & \bm{$243 \pm 6$}\\
 & $(0.1,0.6,0.3)$ & $1489 \pm 12$ & \bm{$549 \pm 3$} & $264 \pm 6$\\
 & $(0.6,0.1,0.3)$ & \bm{$1407 \pm 8$} & $618 \pm 5$ & $270 \pm 6$\\
\hline
 \multirow{3}{*}{\textbf{Map 8}} & $(0.33,0.33,0.33)$ & $1761 \pm 9$ & $254 \pm 5$& $382 \pm 3$\\
 & $(0.1,0.3,0.6)$ & $1804 \pm 10$ & $269 \pm 4$ & \bm{$357 \pm 4$}\\
 & $(0.1,0.6,0.3)$ & $1826 \pm 10$ & \bm{$230 \pm 3$} & $392 \pm 7$\\
 & $(0.6,0.1,0.3)$ & \bm{$1732 \pm 9$} & $311 \pm 8$ & $379 \pm 6$\\
\hline
 \multirow{3}{*}{\textbf{Map 9}} & $(0.33,0.33,0.33)$ & $2501 \pm 14$ & $926 \pm 6$& $574 \pm 9$\\
 & $(0.1,0.3,0.6)$ & $2503 \pm 10$ & $921 \pm 10$ & \bm{$524 \pm 8$}\\
 & $(0.1,0.6,0.3)$ & $2641 \pm 14$ & \bm{$833 \pm 5$} & $574 \pm 14$\\
 & $(0.6,0.1,0.3)$ & \bm{$2470 \pm 9$} & $956 \pm 5$ & $573 \pm 8$\\
\hline
 \multirow{3}{*}{\textbf{Map 10}} & $(0.33,0.33,0.33)$ & $1430 \pm 8$ & $630 \pm 4$& $205 \pm 2$\\
 & $(0.1,0.3,0.6)$ & $1493 \pm 13$ & $615 \pm 4$ & $209 \pm 2$\\
 & $(0.1,0.6,0.3)$ & $1542 \pm 10$ & \bm{$554 \pm 4$} & $229 \pm 5$\\
 & $(0.6,0.1,0.3)$ & \bm{$1378 \pm 5$} & $663 \pm 6$ & $202 \pm 4$\\
\hline
\end{tabular}
\caption{MO-MCTS results in MO-PTSP with different weight vectors. Values in bold indicate the best results on each map, when they are separated at least by $2$ standard errors from the others.}
\label{tab:weights}
\end{center}
\end{table}

@@

>>>>

However, there are some cases where it cannot be said that $\vec x \preceq \vec y$ or $\vec y \preceq \vec x$. 
In this case, it is said that these solutions are indifferent to each other. Solutions that are not dominated can be grouped in a \textit{non-dominated set}. Given a non-dominated set $P$, it is said that $P$ is the \textit{Pareto-set} if there is no other solution in the decision space that dominates any member of $P$. The corresponding objective vectors of the members in the Pareto-set build a so called \textit{Pareto-front}. The relations between decision and objective space, dominance and the non-dominated set are depicted in Figure~\ref{fig:moop}.

@@

A popular choice for multi-objective optimization problems are evolutionary multi-objective optimization (EMO) algorithms~\cite{Coello1999, Zhou2011}. 
The goal of EMO algorithms is to find a set of optimal solutions with a good convergence to the Pareto-front as well as a good spread and diversity along the Pareto-front.
One of the most well-known algorithms in the literature is the Non-dominated Sorting Evolutionary Algorithm II (NSGA-{II})~\cite{Deb2002}, the pseudocode of which is shown in Algorithm~\ref{alg:nsga2}. NSGA-II is known to deliver solutions with very good diversity and convergence to the Pareto-front for 2-objective problems. However, for problems with more than 3 objectives, other approaches such as NSGA-III~\cite{Jain2013}, SMS-EMOA~\cite{Beume2007} and MOEA/D~\cite{Zhang2007a} are shown to outperform NSGA-II. As in any evolutionary algorithm, NSGA-{II} evolves a set of $N$ individuals in a population denoted as $Pop$ with the difference that they are ranked according to a dominance criterion and a crowding distance measure, which are used to maintain a good diversity of solutions. After each iteration of the algorithm, only the best $N$ individuals according to this ranking are maintained to the next generation.

@@

The three main pillars of the NSGA-II algorithm are:
\begin{itemize}
\item Fast non-dominated sorting: The function $F = \Call{fastNonDominatedSort}{U(t)}$ performs a non-dominated sorting and ranks the individuals stored in a set $U$ into several non-dominated fronts denoted as $F_i$, where the solutions in $F_0$ are the non-dominated solutions in the entire set. $F_i$ is the set of non-dominated solutions in $R \setminus (F_0 \cup \cdots \cup F_{i-1})$. 
\item Crowding distance: The function $\Call{crowdingDistanceAssignment}{F_i}$ assigns to each one of the individuals in $F_i$ a crowding distance value, which is the distance between the individual and its neighbours. The individuals with the smallest crowding distances are selected with a lower probability than the ones with larger values.   
\item Elitism: The individuals from the first front $F_0$ are always ranked first, according to the dominance criterion and their crowding distance. This ensures that the best solutions always survive to the next generation.
\end{itemize}

@@

@@

\begin{table}[!t]
\begin{center}
%\begin{tabular}{|>{\centering\arraybackslash}m{0.65cm}|c|c|c|c|}
\begin{tabular}{|p{0.8cm}|p{2.2cm}|m{1.13cm}|m{1.13cm}|m{1.13cm}|}
\hline
\textbf{Map}  & \textbf{$W:(w_t, w_f, w_d)$} & \textbf{Time} &  \textbf{Fuel} & \textbf{Damage} \\ 
\hline
 \multirow{3}{*}{\textbf{Map 1}} & $(0.33,0.33,0.33)$ & $1654 \pm 7$ & $131 \pm 2$& $846 \pm 13$\\
 & $(0.1,0.3,0.6)$ & $1657 \pm 8$ & $130 \pm 2$ & \bm{$773 \pm 11$}\\
 & $(0.1,0.6,0.3)$ & $1681 \pm 11$ & $131 \pm 2$ & $837 \pm 15$\\
 & $(0.6,0.1,0.3)$ & $1649 \pm 8$ & $132 \pm 2$ & $833 \pm 13$\\
\hline
 \multirow{3}{*}{\textbf{Map 2}} & $(0.33,0.33,0.33)$ & $1409 \pm 7$ & $235 \pm 4$& $364 \pm 3$\\
 & $(0.1,0.3,0.6)$ & $1402 \pm 6$ & $236 \pm 5$ & \bm{$354 \pm 2$}\\
 & $(0.1,0.6,0.3)$ & $1416 \pm 8$ & \bm{$219 \pm 4$} & $360 \pm 3$\\
 & $(0.6,0.1,0.3)$ & $1396 \pm 8$ & $245 \pm 5$ & $361 \pm 2$\\
\hline
 \multirow{3}{*}{\textbf{Map 3}} & $(0.33,0.33,0.33)$ & $1373 \pm 6$ & $221 \pm 3$& $301 \pm 7$\\
 & $(0.1,0.3,0.6)$ & $1378 \pm 5$ & $211 \pm 3$ & \bm{$268 \pm 5$}\\
 & $(0.1,0.6,0.3)$ & $1385 \pm 6$ & \bm{$203 \pm 4$} & $291 \pm 7$\\
 & $(0.6,0.1,0.3)$ & \bm{$1363 \pm 4$} & $229 \pm 4$ & $285 \pm 7$\\
\hline
 \multirow{3}{*}{\textbf{Map 4}} & $(0.33,0.33,0.33)$ & $1383 \pm 6$ & $291 \pm 5$& $565 \pm 5$\\
 & $(0.1,0.3,0.6)$ & $1385 \pm 7$ & $304 \pm 4$ & \bm{$542 \pm 4$}\\
 & $(0.1,0.6,0.3)$ & $1423 \pm 6$ & \bm{$273 \pm 4$} & $583 \pm 5$\\
 & $(0.6,0.1,0.3)$ & $1388 \pm 6$ & $309 \pm 4$ & $559 \pm 5$\\
\hline
 \multirow{3}{*}{\textbf{Map 5}} & $(0.33,0.33,0.33)$ & $1405 \pm 7$ & $467 \pm 4$& $559 \pm 4$\\
 & $(0.1,0.3,0.6)$ & $1431 \pm 9$ & $447 \pm 4$ & $541 \pm 4$\\
 & $(0.1,0.6,0.3)$ & $1467 \pm 9$ & \bm{$411 \pm 5$} & $567 \pm 5$\\
 & $(0.6,0.1,0.3)$ & $1399 \pm 9$ & $469 \pm 4$ & $547 \pm 3$\\
\hline
 \multirow{3}{*}{\textbf{Map 6}} & $(0.33,0.33,0.33)$ & $1575 \pm 7$ & $549 \pm 5$& $303 \pm 4$\\
 & $(0.1,0.3,0.6)$ & $1626 \pm 9$ & $540 \pm 6$ & $286 \pm 5$\\
 & $(0.1,0.6,0.3)$ & $1703 \pm 11$ & \bm{$499 \pm 4$} & $316 \pm 7$\\
 & $(0.6,0.1,0.3)$ & $1571 \pm 7$ & $559 \pm 5$ & $294 \pm 4$\\
\hline
 \multirow{3}{*}{\textbf{Map 7}} & $(0.33,0.33,0.33)$ & $1434 \pm 5$ & $599 \pm 6$& $284 \pm 6$\\
 & $(0.1,0.3,0.6)$ & $1475 \pm 10$ & $602 \pm 5$ & \bm{$243 \pm 6$}\\
 & $(0.1,0.6,0.3)$ & $1489 \pm 12$ & \bm{$549 \pm 3$} & $264 \pm 6$\\
 & $(0.6,0.1,0.3)$ & \bm{$1407 \pm 8$} & $618 \pm 5$ & $270 \pm 6$\\
\hline
 \multirow{3}{*}{\textbf{Map 8}} & $(0.33,0.33,0.33)$ & $1761 \pm 9$ & $254 \pm 5$& $382 \pm 3$\\
 & $(0.1,0.3,0.6)$ & $1804 \pm 10$ & $269 \pm 4$ & \bm{$357 \pm 4$}\\
 & $(0.1,0.6,0.3)$ & $1826 \pm 10$ & \bm{$230 \pm 3$} & $392 \pm 7$\\
 & $(0.6,0.1,0.3)$ & \bm{$1732 \pm 9$} & $311 \pm 8$ & $379 \pm 6$\\
\hline
 \multirow{3}{*}{\textbf{Map 9}} & $(0.33,0.33,0.33)$ & $2501 \pm 14$ & $926 \pm 6$& $574 \pm 9$\\
 & $(0.1,0.3,0.6)$ & $2503 \pm 10$ & $921 \pm 10$ & \bm{$524 \pm 8$}\\
 & $(0.1,0.6,0.3)$ & $2641 \pm 14$ & \bm{$833 \pm 5$} & $574 \pm 14$\\
 & $(0.6,0.1,0.3)$ & \bm{$2470 \pm 9$} & $956 \pm 5$ & $573 \pm 8$\\
\hline
 \multirow{3}{*}{\textbf{Map 10}} & $(0.33,0.33,0.33)$ & $1430 \pm 8$ & $630 \pm 4$& $205 \pm 2$\\
 & $(0.1,0.3,0.6)$ & $1493 \pm 13$ & $615 \pm 4$ & $209 \pm 2$\\
 & $(0.1,0.6,0.3)$ & $1542 \pm 10$ & \bm{$554 \pm 4$} & $229 \pm 5$\\
 & $(0.6,0.1,0.3)$ & \bm{$1378 \pm 5$} & $663 \pm 6$ & $202 \pm 4$\\
\hline
\end{tabular}
\caption{MO-PTSP results with different weight vectors. Values in bold indicate the best results on each map, when they are separated at least by $2$ standard errors from the others.}
\label{tab:weights}
\end{center}
\end{table}
